\begin{answer}{ncralgorithm}
Let's use Python again.
Since we want to evaluate
\[
\binom{n}{k} = \frac{n!}{ (n-k)! k! }
\]
we need a function to calculate the factorial.
The  following code uses recursion to calculate it.
\begin{minted}{python}
def factorial(n):
    if n==0:
        return 1
    return(n * factorial(n-1) )

def nCr(n,k):
    return factorial(n)/(factorial(k) * factorial(n-k))
\end{minted}
For big numbers, this is expensive.
We can come up with a smarter solution.
Consider the following example with small integers.
\begin{align*}
\binom{8}{5} &= \frac{8!}{ (8-5)! 5! } \\
             &= \frac{(8 \times 7 \times 6 )}{3!} \\
             &= \frac{8 \times 7 \times 6 }{  3 \times 2 \times 1 }
\text{.}
\end{align*}
Likewise, the general case will be
\begin{align*}
\binom{n}{k}
             &= \frac{n \times (n-1) \times  \ldots \times (k+1) }{ (n-k) \times (n-k-1) \times \ldots \times 1 }
\text{.}
\end{align*}
It is not necessary to call the factorial function three times,
we can evaluate the nominator and denominator separately.

\begin{minted}{python}
def product(number_list):
    prod = 1
    for number in number_list:
        prod = prod*number

    return prod

def nCr_smart(n,k):
    nominator = product(list(range(k+1,n+1)))
    denominator = product(range(1,n-k+1))

    return nominator/denominator
\end{minted}
By sheer luck, the product function will also work for $0$.
The hardest thing is using the \verb+range+ function of Python correctly; it starts at the first number, and iterates to one less than the second number.
If the second number is smaller than the first, it returns an empty list \verb+[]+.
We can further optimise by noting that $\binom{n}{k}=\binom{n}{n-k}$ and always choosing to evaluate the one that is less work (for the function above, we prefer large values of $k$).
\end{answer}
